Identification of protoneutron star g-modes in gravitational-wave data \pcd{[PCD: alt. title]Inference of proto-neutron star properties from gravitational wave data in core-collapse supernovae.}

### 2020-09-15 methods.tex
Comments on the rest

\pcd{We use this model to infer the properties of the simulations in the 
{\it test set} described in in Section \ref{sec:simulations}.}
To develop \pcd{and describe} the method we \pcd{\sout{considered} focus on} the gravitational wave signal
\pcd{of} {\texttt s20S}, originally
sampled at 16384 Hz but resampled at 4096 Hz.
A spectrogram of this signal is shown in Figure \ref{fig:spectrogram} based on
autoregressive estimates \pcd{[CITATION?]}of the local spectra for successive time intervals of 
\textcolor{red}{length 200} with a \textcolor{red}{ 90\%} overlap.
The dominant emission mode corresponds to the PNS oscillation $\mbox{}^2 g_2$-mode. We have
developed a time-frequency method to track the ridge $m(t)$ in the spectrogram,
taking into account that it is monotonically increasing as time goes. 
\pcd{This is a property of the $\mbox{}^2 g_2$-mode, the frequency of which  
increases as the object becomes more massive and compact}.
Starting from either the left- or right-most column of the time-frequency matrix
we identify and trace the sequence of amplitude peaks within a certain frequency
band given the monotonicity constraint. Appendix \ref{app:gmode} is providing more
details on the reconstruction of the $g$ mode ridge.

>>>>

\pcd{We use this model to infer the properties of the simulations in the 
{\it test set} described in in Section \ref{sec:simulations}.}
To \pcd{\sout{develop}  describe} the method we \pcd{\sout{considered} focus on} the gravitational wave signal
\pcd{of} {\texttt s20S}, originally
sampled at 16384 Hz but resampled at 4096 Hz.
A spectrogram of this signal is shown in Figure \ref{fig:spectrogram} based on
autoregressive estimates \pcd{[CITATION?]}of the local spectra for successive time intervals of 
\textcolor{red}{length 200} with a \textcolor{red}{ 90\%} overlap.
The dominant emission mode corresponds to the PNS oscillation $\mbox{}^2 g_2$-mode. We have
developed a time-frequency method to track the ridge $m(t)$ in the spectrogram,
taking into account that it is monotonically increasing as time goes. 
\pcd{This is a property of the $\mbox{}^2 g_2$-mode, the frequency of which  
increases as the object becomes more massive and compact}.
Starting from either the left- or right-most column of the time-frequency matrix
we identify and trace the sequence of amplitude peaks within a certain frequency
band given the monotonicity constraint. Appendix \ref{app:gmode} is providing more
details on the reconstruction of the $g$ mode ridge.

### 2020-09-15 results.tex
update numbers and plots
Comments on the rest

\section{Detection sensitivity with Advanced gravitational wave detectors}
\label{sec:results}

To estimate how accurately we can infer the time evolution of $r=M_{\rm PNS}/R_{\rm PNS}^2$ in the
gravitational wave detector data, we have added {\texttt s20S} GW signal to 
100 Gaussian noise realisations whose power spectral density follows advanced LIGO (aLIGO)
spectrum~\cite{aLIGOsens:2018} shown on Figure~\ref{fig:spectrum}. 
We have varied the distance to the source, covering a large
range of distances for which a detection in second generation of gravitational wave detectors
is feasible. The source is optimally oriented with
respect to the gravitational wave detector. We are assuming a GW signal from a core collapse
phenomena has been identified in the data and that the beginning of the GW signal is known within $O(10~ms)$.
The data (signal embedded in noise) are whitened using the function {\it prewhiten} of the R-package TSA.
An auto-regressive model with maximal \textcolor{red}{100} coefficients has been used.

For each of the noise realisations, we reconstruct the ratio time series {$r_i$}
of length $N$ starting from the left side of the spectrogram and constraining the beginning of the
track to be smaller than \unit[200]{Hz}. The reconstructed ratio is then compare to the ``true'' ratio
{$r_i^0$} derived from the PNS mass and radius generated by the simulation code that produced {\texttt s20S}.

@@

$\Delta$ values of each of the 100 noise realisation are shown as well as function of the distance
on Figure \ref{fig:s20results}. For a source located up to $\sim$\unit[10]{kpc} the relative error
remains smaller than 20\%. At small distance $\Delta$ is small but not null. This reflects the
approximation of the model used for $r$.
It is nevertheless remarkable that one can reconstruct the ratio time series with a good
precision at distance up to $\sim$ 10 kpc for this particular waveform, with $coverage$ value
larger than 80\%.
We have tested that the method does not depend on features of {\texttt s20S} using 7 other waveforms
described in section \ref{sec:simulations} covering a large range of progenitor masses.
Figure \ref{fig:aLIGO_cov_allwvf} shows that apart {\tt s11.2--LS220}, the ratio is well
reconstructed for all waveforms up to $\sim$ 10kpc. On this figure we also show the $coverage$
value in case of absence of signal. The median value is significantly different from 0 because
the g-mode reconstruction algorithm is looking for a continuously frequency increasing track
in the spectrogram, starting between 0 and 200 Hz. In Table \ref{tab:} we are reporting the
distance at which $coverage$ median is lower than 80\%.

@@

 \caption{Boxplots of $coverage$ (upper panel) and $\Delta$ (lower panel) for {\texttt s20S} signal embedded in aLIGO noise at different distances from the Earth. 100 noise realisations is considered for each distance.} \label{fig:s20results}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{plots/aLIGO_cov_allwvfs}
 \caption{Median of $coverage$ for 8 CCSN waveforms embedded in aLIGO noise and located at different distance from the Earth. The ``no signal'' line and band show the median and first and third quartile of $coverage$ in absence of any signal.} \label{fig:aLIGO_cov_allwvf}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{plots/aLIGO_prec_allwvfs}
 \caption{Median of $Delta$ for 8 CCSN waveforms embedded in aLIGO noise and located at different distance from the Earth. The ``no signal'' line and band show the median and first and third quartile of $Delta$ in absence of any signal.} \label{fig:aLIGO_prec_allwvf}
\end{figure}

\begin{table}
  \centering
  \begin{tabular}{c|cccccccc}
    \hline

    Simulation & \texttt{s11} & \texttt{s15} & \texttt{s15S} & \texttt{s15G} & \texttt{s20} & \texttt{s20S} & \texttt{s25}  & \texttt{s40}
    \\   
    \hline
    aLIGO char. & 7  &      26      &    25         &      21       &   16         &    11         &  9           &  12
    \\
    distance (kpc) & & & & & & & &
    \\ 
    \hline
    SNR in aLIGO         & 19.5 &    55.4    &    59.0       &      60.0     &   34.3       &    35.8          & 116.5         & 98.5
    \\
    \hline
    \hline
    CE2  char.  &      &            &                &               &              &                 &               & 
    \\
    distance (kpc) & & & & & & & &
    \\
    \hline
    SNR in CE2      &      &            &                &               &              &                 &               &
    \\
    \hline
    \hline
  \end{tabular}
  \caption{%%
    Matched filter signal-to-noise ratio (SNR) of the simulated waveforms for
    the different GW detectors considered in this study. The source is located
    at 10 kpc and is optimally oriented with respect to the detector.
    %%
  }
  \label{Tab:results}
\end{table}

>>>>

% !TEX root = ccsn.tex
\section{Detection sensitivity with Advanced gravitational wave detectors}
\label{sec:results}

To estimate how accurately we can infer the time evolution of $r=M_{\rm PNS}/R_{\rm PNS}^2$ in the
gravitational wave detector data, we have added \pcd{the} GW signal \pcd{from {\texttt s20S}} to 
100 Gaussian noise realisations whose power spectral density follows \pcd{the} advanced LIGO (aLIGO)
spectrum~\cite{aLIGOsens:2018} shown on Figure~\ref{fig:spectrum}. 
We have varied the distance to the source, covering a large
range of distances for which a detection in second generation of gravitational wave detectors
is feasible. The source is optimally oriented with
respect to the gravitational wave detector. We are assuming a GW signal from a core collapse
phenomena has been identified in the data and that the beginning of the GW signal is known within $O(10~ms)$.
The data (signal embedded in noise) are whitened using the function {\it prewhiten} of the R-package TSA.
An auto-regressive model with maximal \textcolor{red}{100} coefficients has been used.

For each of the noise realisations, we reconstruct the ratio time series {$r_i$}
of length $N$ starting from the left side of the spectrogram and constraining the beginning of the
track to be smaller than \unit[200]{Hz}. The reconstructed ratio is then compare to the ``true'' ratio
{$r_i^0$} derived from the PNS mass and radius \pcd{computed from the \sout{generated by the simulation code that produced} {\texttt s20S} simulation}.

@@

$\Delta$ values of each of the 100 noise realisation are shown as well as function of the distance
on Figure \ref{fig:s20results}. For a source located up to $\sim$\unit[10]{kpc} the relative error
remains smaller than 20\% \pcd{[PCD: should we comment on the outliers?]}. At small distance $\Delta$ is small but not null. This reflects the
approximation of the model used for $r$.
It is nevertheless remarkable that one can reconstruct the ratio time series with a good
precision at distance up to $\sim$ 10 kpc for this particular waveform, with $coverage$ value
larger than 80\%.
We have tested that the method does not depend on features of {\texttt s20S} using \pcd{the} 7 other waveforms \pcd{of the {\it test set}}
described in section \ref{sec:simulations} covering a large range of progenitor masses.
Figure \ref{fig:aLIGO_cov_allwvf} shows that apart {\tt s11.2--LS220}, the ratio is well
reconstructed for all waveforms up to $\sim$ 10kpc. On this figure we also show the $coverage$
value in case of absence of signal. The median value is significantly different from 0 because
the g-mode reconstruction algorithm is looking for a continuously frequency increasing track
in the spectrogram, starting between 0 and 200 Hz. In Table \ref{tab:results} we are reporting the
distance at which $coverage$ median is lower than 80\%.

@@

 \caption{Boxplots of $coverage$ (upper panel) and $\Delta$ (lower panel) for {\texttt s20S} signal embedded in aLIGO noise at different distances from the Earth. 100 noise realisations is considered for each distance.
 \pcd{[PCD: I guess you use "coverage probability" because we are showing the box plots. Shouln't we say $\Delta$ probability as well? Or just "coverage"? Also, 
 how are outliers computed? Why are there so many outliers in $|delta$? If they are a significant fraction of the data points why are they considered outliers?]}}
  \label{fig:s20results}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{plots/aLIGO_coverage_allwvfs}
 \caption{Median of $coverage$ for 8 CCSN waveforms embedded in aLIGO noise and located at different distance from the Earth. The ``no signal'' line and band show the median and first and third quartile of $coverage$ in absence of any signal.} \label{fig:aLIGO_cov_allwvf}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{plots/aLIGO_delta_allwvfs}
 \caption{Median of $Delta$ for 8 CCSN waveforms embedded in aLIGO noise and located at different distance from the Earth. The ``no signal'' line and band show the median and first and third quartile of $Delta$ in absence of any signal.} \label{fig:aLIGO_prec_allwvf}
\end{figure}

\begin{table}
  \centering
  \begin{tabular}{c|c|cccccccc}

\multicolumn{2}{c|}{}  & \texttt{s11} & \texttt{s15} & \texttt{s15S} & \texttt{s15G} & \texttt{s20} & \texttt{s20S} & \texttt{s25}  & \texttt{s40}\\

\hline
\multirow{2}{*}{aLIGO} & $d_{max}$ (kpc) & 7.3  & 26.3 & 24.8 & 22.3 & 16.3 & 10.8 & 7.8  & 14.8\\
\cline{2-10}
                       & SNR            & 13.0 & 37.0 & 38.7 & 39.2 & 22.9 & 23.3 & 75.6 & 63.6\\
\hline
\hline

  \end{tabular}
  \caption{%%
    Matched filter signal-to-noise ratio (SNR) of the simulated waveforms for
    the different GW detectors considered in this study. The source is located
    at 10 kpc and is optimally oriented with respect to the detector.
    %%
  }
  \label{tab:results}
\end{table}
